Sketch Recogniton using Particle Swarm Algorithm

### 2009-04-07 draft/System.tex
april 7

\chapter{System Details}
\label{sec:SystemDetails}

@@

   where $E_{ellipse}$ is the error computed by Equation(\ref{eq:circleFit}) and $E_{area}$ is computed as the difference between the actual area of the stroke and the area of the estimated ellipse Equation(\ref{eq:ErrorArea}). If confidence value $Conf$ is less than threshold $th_{Ellipse}$\footnote{The threshold used is $th_{Ellipse}=0.7$ } then the stroke is segmented as an ellipse otherwise the system proceeds proceed to the two PSO segmentation algorithms. % The confidence value is used to label the stroke as ellipse or un segmented stroke. If the stroke as un-segmented the next process will be to pass the stroke into curve segmentation algorithm.

   The next section describes the \textit{Discrete Particle Swarm Algorithm (DPSO)} then it proceeds to detail the two DPSO segmentation algorithms.

@@

\subsection{Discrete Particle Swarm Algorithm}
\label{sec:ParticleSwarmAlgorithm}
%\section{Particle Swarm Algorithm}
%\label{PSO}
%What is particle swarm algorithm and how it was used in related researches. 
The main idea of \textit{Particle Swarm Algorithm (PSO)} is to represent each agent with a particle from the solution space \cite{PSOFirst}. Each agent moves the particle with a direction and velocity $v_{ij}$ based on equations \ref{eq:Swarm} \& \ref{eq:Swarm1}.
\begin{equation}
%\[
p_{ij}=p_{ij}+v_{ij},
%\
\label{eq:Swarm1}
\end{equation}
where $p_{ij}$ represent the $jth$ particle in the $ith$ agent and $v_{ij}$ is the velocity of the $jth$ particle in the $ith$ agent.
 %Equation [\ref{eq:Swarm}] shows how velocity and direction of each particle are computed
 \begin{equation}
v_{ij}  = v_{ij}  + c_1 r_1 (lbest_{ij}  - p_{ij} ) + c_2 r_2 (gbest_{ij}  - p_{ij} )
\label{eq:Swarm}
\end{equation}
 where $lbest_{ij}$ is the local best particle, $gbest_{ij}$ is the global best particle, $r_1$ \& $r_2$ are random variables and $c_1$ \& $c_2$ are the swarm system variables.
 After each iteration the global best $g_{best}$ particle and the agent local best $l_{best}$ particle are evaluated based on the maximum fitness functions of all particles in the solution space. The solution is found after achieving a specific number of iteration or after an error threshold is achieved.
Equation \ref{eq:descrite}  
\begin{equation}
   P(i)\Leftarrow 
\{
\begin{array}{c} 
1 \quad \quad if\quad r_{3}>p_{i}  \\

0 \quad \quad if\quad r_{3}<p_{i} 
\label{eq:descrite}
\end{array}\}
\end{equation}
 where $p_{ij}$ is the numerical values of the particle and $r_{3}$ is a random variable, is used to change the general swarm algorithm into binary particle (\textit{Discrete Particle Swarm Algorithm DPSO}) which handles particle values of either $0$ or $1$ \cite{PSODisceret}.  
\subsection{Swarm Segmentation}
\label{sec:SwarmSegmentation}
Two DPSO algorithms generate two different segmentations for each stroke. Each DPSO algorithms tries to find the best particle in the solution space. Both algorithms has the same problem formulation but different fitness functions. After generating two segmentations the system chooses the best segmentation from the outputs of the DPSO. The details of the problem formulation and fitness functions are in the following sections.
%In this process the system generate two stroke segmentation using two PSO segmentation algorithm. The system generates segmentation from both algorithms and then chooses the segmentation with the minimum error value. The problem definition is the same in both algorithms but they differ in the fitness function and the error functions. %formation is nearly the same in both. 
\subsubsection{Problem Formulation}
\label{sec:ProblemFormulation}
The input stroke with $N$ points can be represented by set $S = \left\{ {x_1 ,x_2  \ldots x_N } \right\}$ where $x_i$ is the location of the point $i$ . The swarm algorithms consist of $M$ agents which are represented by the set 
$A  = \left\{ {P_i \left| {i = 1,2 \cdots M} \right.} \right\}$ where $P_i$ is a single solution particle from the solution space. Each particle decodes the problem with binary array with the same length $N$ as the input stroke (Figure \ref{fig:CodingSwarm}).   
\begin{figure}
	\centering
		\includegraphics{images/CodingSwarm.eps}
	\caption{An Example Stroke and the Coding}
	\label{fig:CodingSwarm}
\end{figure}
% The particles of the swarm represent a single solution of the solution space. For this problem the, each particle %will give a different segmentation for the input stroke. Firstly, we will define the stroke with N points by the set %S where.  We define the arc %An array with the same length as the number of points of the strokes.
The system represents each particle $P_i$ by $P_i = \left\{ {p_{ij} \left| {j = 1,2 \cdots N} \right.} \right\}$ where $p_{ij}$ is either 0 or 1 where $p_{ij}=1$ means that point $j$ is a dominant point(see Figure \ref{fig:CodingSwarm}.  Thus , the particle represents points that are chosen to be used as dominant points for this segmentation. 
The goal of the DPSO algorithm is to find the solution $P_i$ that generates the minimum set of dominate points that defines the stroke with minimum segmentation error. In other words, the system tries to find the fewer number of points (1's) location in the particle array which gives minimum segmentation error.

>>>>

%\chapter{System Details}
%\label{sec:SystemDetails}

@@

   where $E_{ellipse}$ is the error computed by Equation(\ref{eq:circleFit}) and $E_{area}$ is computed as the difference between the actual area of the stroke and the area of the estimated ellipse Equation(\ref{eq:ErrorArea}). If confidence value $Conf$ is less than threshold $th_{Ellipse}$\footnote{The threshold used is $th_{Ellipse}=0.7$ } then the stroke is segmented as an ellipse otherwise the system proceeds proceed to the two DPSO segmentation algorithms. % The confidence value is used to label the stroke as ellipse or un segmented stroke. If the stroke as un-segmented the next process will be to pass the stroke into curve segmentation algorithm.

 %  The next section describes the \textit{Discrete Particle Swarm Algorithm (DPSO)} then it proceeds to detail the two DPSO segmentation algorithms.

@@

%\subsection{Discrete Particle Swarm Algorithm}
%\label{sec:ParticleSwarmAlgorithm}
%%\section{Particle Swarm Algorithm}
%%\label{PSO}
%%What is particle swarm algorithm and how it was used in related researches. 
%The main idea of \textit{Particle Swarm Algorithm (PSO)} is to represent each agent with a particle from the solution space \cite{PSOFirst}. Each agent moves the particle with a direction and velocity $v_{ij}$ based on equations \ref{eq:Swarm} \& \ref{eq:Swarm1}.
%\begin{equation}
%%\[
%p_{ij}=p_{ij}+v_{ij},
%%\
%\label{eq:Swarm1}
%\end{equation}
%where $p_{ij}$ represent the $jth$ particle in the $ith$ agent and $v_{ij}$ is the velocity of the $jth$ particle in the $ith$ agent.
% %Equation [\ref{eq:Swarm}] shows how velocity and direction of each particle are computed
% \begin{equation}
%v_{ij}  = v_{ij}  + c_1 r_1 (lbest_{ij}  - p_{ij} ) + c_2 r_2 (gbest_{ij}  - p_{ij} )
%\label{eq:Swarm}
%\end{equation}
% where $lbest_{ij}$ is the local best particle, $gbest_{ij}$ is the global best particle, $r_1$ \& $r_2$ are random variables and $c_1$ \& $c_2$ are the swarm system variables.
% After each iteration the global best $g_{best}$ particle and the agent local best $l_{best}$ particle are evaluated based on the maximum fitness functions of all particles in the solution space. The solution is found after achieving a specific number of iteration or after an error threshold is achieved.
%Equation \ref{eq:descrite}  
%\begin{equation}
%   P(i)\Leftarrow 
%\{
%\begin{array}{c} 
%1 \quad \quad if\quad r_{3}>p_{i}  \\
%
%0 \quad \quad if\quad r_{3}<p_{i} 
%\label{eq:descrite}
%\end{array}\}
%\end{equation}
% where $p_{ij}$ is the numerical values of the particle and $r_{3}$ is a random variable, is used to change the general swarm algorithm into binary particle (\textit{Discrete Particle Swarm Algorithm DPSO}) which handles particle values of either $0$ or $1$ \cite{PSODisceret}.  
\subsection{Swarm Segmentation}
\label{sec:SwarmSegmentation}
Two DPSO algorithms generate two different segmentations for each stroke. Each DPSO algorithms tries to find the best particle in the solution space. Both algorithms has the same problem formulation but different fitness functions. After generating two segmentations the system chooses the best segmentation from the outputs of the DPSO. The details of the problem formulation and fitness functions are in the following sections.
%In this process the system generate two stroke segmentation using two PSO segmentation algorithm. The system generates segmentation from both algorithms and then chooses the segmentation with the minimum error value. The problem definition is the same in both algorithms but they differ in the fitness function and the error functions. %formation is nearly the same in both. 
\subsubsection{Problem Formulation}
\label{sec:ProblemFormulation}
The input stroke with $N$ points can be represented by set $S = \left\{ {x_1 ,x_2  \ldots x_N } \right\}$ where $x_i$ is the location of the point $i$ . The swarm algorithms consist of $M$ agents which are represented by the set 
$A  = \left\{ {P_i \left| {i = 1,2 \cdots M} \right.} \right\}$ where $P_i$ is a single solution particle from the solution space. Each particle decodes the problem with binary array with the same length $N$ as the input stroke (Figure \ref{fig:CodingSwarm}).   
\begin{figure}
	\centering
		\includegraphics{images/CodingSwarm.eps}
	\caption{An Example Stroke and the Coding}
	\label{fig:CodingSwarm}
\end{figure}
% The particles of the swarm represent a single solution of the solution space. For this problem the, each particle %will give a different segmentation for the input stroke. Firstly, we will define the stroke with N points by the set %S where.  We define the arc %An array with the same length as the number of points of the strokes.
The system represents each particle $P_i$ by $P_i = \left\{ {p_{ij} \left| {j = 1,2 \cdots N} \right.} \right\}$ where $p_{ij}$ is either 0 or 1 where $p_{ij}=1$ means that point $j$ is a dominant point(see Figure \ref{fig:CodingSwarm}.  Thus , the particle represents points that are chosen to be used as dominant points for this segmentation. 
The goal of the DPSO algorithm is to find the solution $P_i$ that generates the minimum set of dominate points that defines the stroke with minimum segmentation error. In other words, the system tries to find the fewer number of points (1's) location in the particle array which gives minimum segmentation error.

### 2009-04-07 draft/chapterSurvey.tex
april 7

\section{Introduction }
\label{sec:Introduction}

A wide variety of techniques were suggested for sketch recognition. Currently symbol recognition is solved as an either image based and feature based or AI-based problem. In image based recognition symbols are recognized based on there goemetrical, structure or other spatial features. 
%The AI based recognition treat the problem as a methods in recognizing symbols mainly imply more time and processing as for the search and rules applied but claims to be more accurate.

@@

\subsection{Pre processing }
\label {sec:preprocessing}
 A stroke is all the points that lie along the path of the user pen from the moment of his pen down to pen up events. Not all those points are important even more, there may be redundance points. Therefore, those strokes will need some preprocessing.

@@

\cite{Mathpad46}Handle rotations invariant using polar transformation then shifting to make it more reliable when template matching. However, they state that the only problem to there system is that the points near the centroid affect the polar transformations which will effect the matching. %(To solve it they say that loosing the weight of the pixel near the centroid will improve classification).

@@

From the image-based view the symbol is a sequences of line segments or/and curves. To do so without constraining the user drawing style we have to easily divide the user drawn strokes.

@@

\subsubsection{Removing noise}
\label{sec:RemovingNoise}

@@

\subsection{Image Based Classification}
\label{sec:Image Based Classification}

@@

>>>>

%\section{Introduction }
%\label{sec:Introduction}
The history of pen and sketch based computing goes back to 1963 with Ivan Sutherland's SKETCHPAD \cite{}, which used a light pen to draw on the monitor to create circuit diagrams. Rubine \cite{} Guesture recognition system.

In this chapter, we will compare our system with some of the systems that support free-hand sketching. In general, these systems lack either one or more of the following properties that we believe a sketching system should have:
\begin{enumerate}
	\item It should be possible to draw arbitrary shapes with a single stroke, (i.e., without requiring the user to draw objects in pieces).
\item It should be possible using multiple strokes without a specific order, style or orientation. 
\item The system should do automatic stroke segmenation. The user should not ave to specify vertex positions manually. 
\item The sketching should be as natural as possible. 
\end{enumerate}
A wide variety of techniques were suggested for sketch recognition. Currently symbol recognition is solved as an either image based and feature based or AI-based problem. In image based recognition symbols are recognized based on there goemetrical, structure or other spatial features. 
%The AI based recognition treat the problem as a methods in recognizing symbols mainly imply more time and processing as for the search and rules applied but claims to be more accurate.

@@

\section{Pre processing and Segmentation}
\label {sec:preprocessing}
% A stroke is all the points that lie along the path of the user pen from the moment of his pen down to pen up events. Not all those points are important even more, there may be redundance points. Therefore, those strokes will need some preprocessing.

@@

%\cite{Mathpad46} Handle rotations invariant using polar transformation then shifting to make it more reliable when template matching. However, they state that the only problem to there system is that the points near the centroid affect the polar transformations which will effect the matching. %(To solve it they say that loosing the weight of the pixel near the centroid will improve classification).

@@

%From the image-based view the symbol is a sequences of line segments or/and curves. To do so without constraining the user drawing style we have to easily divide the user drawn strokes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%This secton will be removed only mention the mean shift to be replaced by 
In \cite{meanshift10,domainindependent17}, Bo Yu uses mean shift procedure as a noise remover and preprocessing step to the recognition step. The mean shift procedure is simply shifting the point to the average of its neighborhoods so smoothing out the noise without changing the global structure of data.  This process is clamed to help find critical points easily after that.  %% now add the othero one in that used gaussian filter .. and sayit smooths the cruves....

 \cite {overtraced24} tried to solve the over traced strokes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Removing noise}
\label{sec:RemovingNoise}

@@

\section{Sketch recogntion task}
\label{sec:sketchRecogntionTask}
\subsection{Image Based Classification}
\label{sec:Image Based Classification}

@@

\chapter{Particle Swram Optimization}
\label{sec:ParticleSwramOptimization}

\section{Particle Swram Optimization Review}
\label{sec:ParticleSwramOptimizationReview}

%review on the pso alogrithm alone.................

\section{Discrete Particle Swarm Algorithm}
\label{sec:ParticleSwarmAlgorithm}
%\section{Particle Swarm Algorithm}
%\label{PSO}
%What is particle swarm algorithm and how it was used in related researches. 
The main idea of \textit{Particle Swarm Algorithm (PSO)} is to represent each agent with a particle from the solution space \cite{PSOFirst}. Each agent moves the particle with a direction and velocity $v_{ij}$ based on equations \ref{eq:Swarm} \& \ref{eq:Swarm1}.
\begin{equation}
%\[
p_{ij}=p_{ij}+v_{ij},
%\
\label{eq:Swarm1}
\end{equation}
where $p_{ij}$ represent the $jth$ particle in the $ith$ agent and $v_{ij}$ is the velocity of the $jth$ particle in the $ith$ agent.
 %Equation [\ref{eq:Swarm}] shows how velocity and direction of each particle are computed
 \begin{equation}
v_{ij}  = v_{ij}  + c_1 r_1 (lbest_{ij}  - p_{ij} ) + c_2 r_2 (gbest_{ij}  - p_{ij} )
\label{eq:Swarm}
\end{equation}
 where $lbest_{ij}$ is the local best particle, $gbest_{ij}$ is the global best particle, $r_1$ \& $r_2$ are random variables and $c_1$ \& $c_2$ are the swarm system variables.
 After each iteration the global best $g_{best}$ particle and the agent local best $l_{best}$ particle are evaluated based on the maximum fitness functions of all particles in the solution space. The solution is found after achieving a specific number of iteration or after an error threshold is achieved.
Equation \ref{eq:descrite}  
\begin{equation}
   P(i)\Leftarrow 
\{
\begin{array}{c} 
1 \quad \quad if\quad r_{3}>p_{i}  \\

0 \quad \quad if\quad r_{3}<p_{i} 
\label{eq:descrite}
\end{array}\}
\end{equation}
 where $p_{ij}$ is the numerical values of the particle and $r_{3}$ is a random variable, is used to change the general swarm algorithm into binary particle (\textit{Discrete Particle Swarm Algorithm DPSO}) which handles particle values of either $0$ or $1$ \cite{PSODisceret}.
